### 2019-09-13 README.Rmd
Made edits to step 3 of README and vignette

The *diffEnrich* function will merge the results from the *pathEnrich* calls generated above. Specifically, the data frame
'list1_pe' and the data frame 'list2_pe' will be merged using the base *merge* functionality and be merged by the following columns:
'c("KEGG_PATHWAY_ID", "KEGG_PATHWAY_description", "KEGG_PATHWAY_cnt", "KEGG_DATABASE_cnt")'. This merged data set will then be used to perform differential enrichment using the same method and p-value calculation as described above. Users do have the option of choosing a method 
for multiple testing adjustment.

@@

The result of the *diffEnrich* call is the merged data frame with the estimated odds ratio generated by the Fisher's Exact test 
and the associated p-value. Users can choose from those supported by *stats::p.adjust*, and the default is the False Discovery Rate (Benjamini and Hochberg, [1995](http://www.jstor.org/stable/2346101)).

>>>>

The *diffEnrich* function will merge two results from the *pathEnrich* calls generated above. Specifically, the data frame
'list1_pe' and the data frame 'list2_pe' will be merged by the following columns:
"KEGG_PATHWAY_ID", "KEGG_PATHWAY_description", "KEGG_PATHWAY_cnt", "KEGG_DATABASE_cnt". This merged data set will then be used to perform differential enrichment using the same method and p-value calculation as described above. Users do have the option of choosing a method 
for multiple testing adjustment. Users can choose from those supported by *stats::p.adjust* for multiple correction options, and the default is the False Discovery Rate (Benjamini and Hochberg, [1995](http://www.jstor.org/stable/2346101)).

@@

The result of the *diffEnrich* call is a data frame with the estimated odds ratio generated by the Fisher's Exact test 
and the associated p-value.
